\documentclass[margin,line]{res}


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\usepackage{color}
\usepackage{amsfonts} 
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}
\urlstyle{same}

\begin{document}

\name{Sanghyun Kim \vspace*{.1in}}

\begin{resume}

\section{\sc Current Affiliation}

\textbf{Senior Researcher}, Dept. of AI Machinery, \\
System Engineering Research Division, \\
Korea Institute of Machinery \& Materials (KIMM) 
%\\
%\textbf{Visiting Researcher} (until 2019.6) at the Gepetto Team,\\
%Laboratory for Analysis and Architecture of Systems (LAAS), \\
%Centre National de la Recherche Scientifique (CNRS) 

%Research Associate at Stanford Artificial Intelligence Laboratory\\
%Computer Science Department, Stanford University

\section{\sc Contact Information}
%\vspace{.05in}
%\begin{tabular}{@{}p{2in}p{4in}}
%Gates 122             & {\it Phone:}  (650) 796-9566 \\            
%Stanford University & {\it E-mail:}  park73@ai.stanford.edu\\       
%Stanford, CA  94305 USA  & {\it WWW:} ai.stanford.edu/\verb+~+park73 \\     
%\end{tabular}
{\it Address:} 105/7 Causewayside, Edinburgh, United Kingdomg\\
{\it E-mail:}  sanghyun.kim@ed.ac.uk\\       
{\it Phone:}  +44-07305-403313\\            
{\it WWW:}  \url{http://ggory15.github.io} \textit{(for my projects)}, \url{http://github.com/ggory15} \textit{(for source codes)}



%%\section{\sc Objective}
%%Seeking a research position in the area of modeling/analysis, or AI/control for
%%complex dynamical systems.

\section{\sc Education}

{\bf Seoul National University}, Seoul, Korea  \hfill {\bf 2012.3 - 2020.2} \\
\vspace*{-.1in}
\begin{list1}
\vspace*{-.05in}
\item[] Ph.D.  of Dept of Trandisciplinary Studies 
\begin{list2}
%\vspace*{.05in}
\item Lab: Dynamic Robotic System Lab (DYROS Lab, \url{https://dyros.snu.ac.kr})
\item Advisor: Professor Jaeheung Park (park73@snu.ac.kr)
\end{list2}
\end{list1}

{\bf Seoul National University}, Seoul, Korea  \hfill {\bf 2005.3 - 2012.2} \\
%{\em Department of Aeronautics and Astronautics} 
\vspace*{-.1in}
\begin{list1}
\vspace*{-.05in}
\item[] B.A., Mechanical Engineering,  March, 2012
\end{list1}

\section{\sc Research \\Experience}

{\bf University of Edinburgh}, United Kingdom  \hfill {\bf 2020.4 - 2020.9} \\
\vspace*{-.1in}
\begin{list1}
\vspace*{-.05in}
\item[] Research Associate (Post-doctoral Researcher)
\begin{list2}
\item Lab:  Statistical Machine Learning and Motor Control Group (\url{http://web.inf.ed.ac.uk/slmc})
\item Advisor: Prof. Sethu Vijayakumar (sethu.vijayakumar@ed.ac.uk)
\end{list2}
\end{list1}

{\bf Centre National de la Recherche Scientifique (CNRS)}, France  \hfill {\bf 2018.8 - 2019.6} \\
\vspace*{-.1in}
\begin{list1}
\vspace*{-.05in}
\item[] Visiting Researcher
\begin{list2}
\item Lab: Gepetto Team (\url{http://projects.laas.fr/gepetto})
\item Advisor: Dr. Nicolas Mansard (nmansard@laas.fr)
\item Funding: Korean government grant
\end{list2}
\end{list1}

{\bf Gwangju Institute of Science and Technology (GIST)}, Korea  \hfill {\bf 2010.6  - 2010.9} \\
\vspace*{-.1in}
\begin{list1}
\vspace*{-.05in}
\item[] Student Internship
\begin{list2}
\item Lab: Haptic Team (\url{http://dyconlab.gist.ac.kr})
\item Advisor: Prof. Jeha Ryu (ryu@gist.ac.kr)
\end{list2}
\end{list1}

\section{\sc Research\\ Interests}
\textbf{Hierarchical whole-body control} of bipedal robot and mobile-based humanoid \\
\textbf{Task and contact transition algorithm} for hierarchical controller \\
\textbf{Torque-based task space control} \\
\textbf{Whole-body planning} for high redundant robot \\
\textbf{Dexterous robot hand control} \\
\textbf{Manipulation of redundant robotic system} 

\section{\sc Research\\ Experience}
{\bf During visiting researcher in Gepetto Team, LAAS-CNRS, France}
 
\vspace{-.3cm}
\textbf{\emph {Whole-body Planning for Humanoid}} \hfill {\bf 2018 - Presence}
\begin{list2}
\item (Ongoing Work) Generating contact sequence, CoM trajectory, feet trajectories, and whole-body trajectory for legged robots. 
\begin{itemize}
\vspace*{-.05in}
\item[\checkmark] Video: \url{https://youtu.be/JpwigzMQg6E}
\vspace*{-.05in}
\end{itemize}
\item Implementation of CoM trajectory generator based on \textit{Time Optimization}.
\item Implementation of feet trajectories using the concept of hyper-plane.
\item Implementation of Quadratic Programming (QP)-based whole-body planner in C++ and Python: 
\begin{itemize}
\vspace*{-.05in}
\item[\checkmark] Video: \url{https://youtu.be/nHiLV89cMG8}
\vspace*{-.05in}
\item[\checkmark] Codes: \url{https://github.com/ggory15/tsid_python_binding}
\vspace*{-.05in}
\end{itemize}
\end{list2}

\textbf{\emph { Model Predictive Control for Humanoid}} \hfill {\bf 2018 - Presence}
\begin{list2}
\item (Ongoing Work) Developing whole-body controller using Differential Dynamic Programming (DDP).
\item (Ongoing Work) Implementation of DDP-based controller with the collision avoidance constraint.
\begin{itemize}
\vspace*{-.05in}
\item[\checkmark] (Preliminary) Video : \url{https://youtu.be/rq3dXdt8t0E}
\vspace*{-.05in}
\end{itemize}
\end{list2}


{\bf During Ph.D. student}
 
\vspace{-.3cm}


\textbf{\emph { Multiple Task Execution Algorithm}} \hfill  {\bf 2017  - 2020}
\begin{list2}
\item Dynamic task transition algorithm to generate complex behavior.
\item Continuous transitions between arbitrary tasks using the activation parameter [J5].
\begin{itemize}
\vspace*{-.05in}
\item[\checkmark] Insertion and removal both equality and inequality tasks without discontinuity of the control input.
\vspace*{-.05in}
\item[\checkmark] Development of avoidance tasks including joint-limit, singularity, and obstacle.
\vspace*{-.05in}
\item[\checkmark] Video : \url{https://youtu.be/-lfnLhmSk3M}
\vspace*{-.05in}
\item[\checkmark] Codes: \url{https://ggory15.github.io/tasktransition-project}
\vspace*{-.05in}
\end{itemize}
\item (Ongoing Work) Applying the task transition method to operate mobile-based humanoid
\begin{itemize}
\vspace*{-.05in}
\item[\checkmark] Development controller for archiving complex tasks [C8]
\vspace*{-.05in}
\item[\checkmark] Self-collision avoidance algorithm using the concept of attractive force [O1]
\vspace*{-.05in}
\item[\checkmark] Video : \url{https://youtu.be/K8RnMAA0rg4}
\vspace*{-.05in}
\end{itemize}
\item (Ongoing Work) Multi-contact transition for humanoids using Gravito-Inertial Wrench Cone (GIWC)
\end{list2}

\textbf{\emph { Whole-body Control of Torque-controlled Humanoids}} \hfill {\bf 2014 - Presence}
\begin{list2}
\item Design and development of torque-controlled humanoid, DYROS-Red [C2].
\begin{itemize}
\vspace*{-.05in}
\item[\checkmark] EtherCAT and RTX programming for real-time control
\vspace*{-.05in}
\item[\checkmark] High-level controller: Whole-body controller
\vspace*{-.05in}
\item[\checkmark] Low-level controller: Elmo motion controller
\vspace*{-.05in}
\item[\checkmark] Video : \url{https://youtu.be/01E-rKixNfE}
\vspace*{-.05in}
\end{itemize}
\item Implementation of whole-body controllers for torque-controlled humanoids.
\begin{itemize}
\vspace*{-.05in}
\item[\checkmark] Using operational-space controller [C2]
\vspace*{-.05in}
\item[\checkmark] Using hierarchical QP-based controller [J4, J6]
\vspace*{-.05in}
\item[\checkmark] Using DDP-based controller
\vspace*{-.05in}
\end{itemize}
\item (Ongoing Work) Development contact force generator with multi-constraints for dynamic balance. 
\end{list2}

\textbf{\emph { Control of Position-controlled Humanoids}} \hfill {\bf 2014  - 2018}
\begin{list2}
\item Design and development of position-controlled humanoid, DYROS-Jet [J2, J4].
\begin{itemize}
\vspace*{-.05in}
\item[\checkmark] RS-232 communication with 200 Hz
\vspace*{-.05in}
\item[\checkmark] High-level controller: Jacobian-based controller
\vspace*{-.05in}
\item[\checkmark] Low-level controller: Robotis controller
\vspace*{-.05in}
\item[\checkmark] Video : \url{https://youtu.be/9UwJQREUjtc}
\vspace*{-.05in}
\end{itemize}
\item Implementation of inverse kinematics controllers for position-controlled humanoids
\begin{itemize}
\vspace*{-.05in}
\item[\checkmark] using Jacobian-based inverse kinematics controller [J2, J4, C3, W2]
\vspace*{-.05in}
\item[\checkmark] using Forward And Backward Reaching Inverse Kinematics (FABRIK) [C7]
\vspace*{-.05in}
\item[\checkmark] using Recursive Neural Network (RNN) [C5]
\vspace*{-.05in}
\end{itemize}
\item Disturbance observer to enhance balancing performance [C6]
\begin{itemize}
\vspace*{-.05in}
\item[\checkmark] Feed-forward joint disturbance observer for compliant motion
\vspace*{-.05in}
\item[\checkmark] Video:  \url{https://youtu.be/LHGxx0M9ijs}
\vspace*{-.05in}
\end{itemize}
\end{list2}


\textbf{\emph {Singularity avoidance algorithm}} \hfill {\bf 2016  - 2017}
\begin{list2}
\item Comparative analysis of six representative singularity avoidance algorithms:
\\ Damped Pseudo Inverse, Error Damped Pseudo Inverse, Jacobian Transpose, Selectively Damped Inverse, Filtered Inverse, and Task Transition Method
\end{list2}

\textbf{\emph { Development of humanoid system for DRC Finals 2015}} \hfill {\bf 2014  - 2016}
\begin{list2}
\item {Student leader} of Team SNU 
\begin{itemize}
\vspace*{-.05in}
\item[\checkmark] Managing the whole framework of robot
\vspace*{-.05in}
\item[\checkmark] Developing the upper-body and lower-body position controller
\vspace*{-.05in}
\end{itemize}
\item No falling down during the competitions and 12th in DRC Finals 2015 [J2, J4, C3, W2]
\begin{itemize}
\vspace*{-.05in}
\item[\checkmark] Video: \url{https://youtu.be/aWpyfKkbzf0}
\vspace*{-.05in}
\end{itemize}
\end{list2}

\textbf{\emph { Artificial intelligence robot CPR system}} \hfill {\bf 2014  - 2016}
\begin{list2}
\item Robot manipulator to perform CPR in emergency situations [P2, J3]
\item Automatic System based biological data from a patient
\item Simulation on mannequin and animal test
\begin{itemize}
\vspace*{-.05in}
\item[\checkmark] Video: \url{https://youtu.be/D9saZERvzf8}
\vspace*{-.05in}
\end{itemize}
\end{list2}

\textbf{\emph { Robot hand tele-operation control}} \hfill {\bf 2012  - 2014}
\begin{list2}
\item Robot hand synergy mapping using multi-factor model [P1, J1, W1]
\item Extracting synergy by considering individual characteristic as well as grasping motion
\begin{itemize}
\vspace*{-.05in}
\item[\checkmark] Video: \url{https://youtu.be/QzGgV9KHaZI}
\vspace*{-.05in}
\end{itemize}
\item Grasping Force Estimation using sEMG signals [J5]
\end{list2}

\textbf{\emph { Tele-opeartion control of ultrasonic examination system}} \hfill {\bf 2012  - 2013}
\begin{list2}
\item Tele-operated robotic arm for remote ultra-sound exam
\item Automated orientation control for ultrasound
\item Contact force feedback using haptic device
\begin{itemize}
\vspace*{-.05in}
\item[\checkmark] Video: \url{https://youtu.be/_OSkL5e70fI}
\vspace*{-.05in}
\end{itemize}
\end{list2}

{\bf During internship in GIST, Korea}
 
\vspace{-.3cm}
\textbf{\emph { Friction and Gravity Compensator for Surgery Simulator }} \hfill {\bf 2010.6  - 2010.9}
\begin{list2}
\item Research and development on the Laparoscopic simulator 
\item Haptic Feedback using friction and gravity compensator [C1]
\end{list2}


\section{\sc Technical skills}
{\bf Hardware  Experience} \\
\textbf{\emph { Human-sized Humanoids}}
\begin{list2}
\item Torque controlled robot, \textit{DYROS-Red}
\item Position controlled robot, \textit{DYROS-Jet}
\item Torque controlled robot, \textit{TALOS (PAL Robotics Co.)}
\item Position controlled robot, \textit{HRP-2}
\end{list2}
\vspace{-0.3cm}

\textbf{\emph { Mobile-based Humanoids}}
\begin{list2}
\item Four-wheeled mobile base, \textit{Husky}, with 7-DoF arm, \textit{Franka Panda}
\end{list2}
\vspace{-0.3cm}

\textbf{\emph { Manipulator}}
\begin{list2}
\item 7-DoF arm, \textit{Franka Panda}
\item 6-DoF arm, \textit{Roman-3D}
\item 6-DoF arm, \textit{Denso Arm}
\end{list2}
{\bf Software Experience} \\
\textbf{\emph { Programming Skills}}
\begin{list2}
\item Intermediate C++, Python, and Matlab programming for robotics (Windows, Ubuntu 18.04)
\item V-Rep, MuJoCo, Gazebo, and PyBullet for robotic simulation
\end{list2}
\vspace{-0.3cm}
\textbf{\emph { Libraries}}
\begin{list2}
\item Math - Eigen, Lapack, MKL
\item Optimization - qpOASES, Eiquadprog, IFOPT and IPOPT
\item Robot Kinematics and Dynamics: Pinocchio, RBDL
\item Others: Boost (in particular, boost-python), FCL
\end{list2}

\section{\sc Honors and Awards} 
\textbf{Best thesis award} from Seoul National University, 2020.\\
\textbf{Best conference paper award} in IEEE/ASME International Conference on Advanced Robotics and Mechatronics, 2019.\\
\textbf{Korean government grant} for Visiting Scholar of LAAS-CNRS, 2018. \\
\textbf{Best paper award} in Journal of Korea Robotics Society (JKROS), 2018.\\
\textbf{Cum laude} from Dept. of Mechanical Engineering at Seoul National University, 2012. 


\section{\sc Patents} 
[P2]  \textbf{Sanghyun Kim} \textit{et al}. Automatic cardiopulmonary resuscitation device and control method therefor, US Patent, No. 20190029919A1, CN Patent, No. 108697572A, EU Patent, No. 3409258A1, 2019

[P1] \textbf{Sanghyun Kim}, {Jaeheung Park}, Mingon Kim, Jimin Lee, Jounghuem Kwon, Bumjae You. 
APPARATUS FOR ESTIMATING GRASPING POSTURE AND GRASPING FORCE.
Korea Patent, No.10-2016-0075150, 2016.

%\vspace*{-2.5mm}
%NSF Vertical Integration of Research and Education in Statistics and
%Mathematical Sciences\\ (VIGRE) teaching fellowship.
%

\section{\sc International Journal Articles}
[J6] S. Hong, K. Jang, \textbf{S. Kim}, and J. Park.
Regularized Hierarchical Quadratic Program for Real-Time Whole-Body Motion Generation ,
IEEE/ASME Transactions on Mechatronics, 2020. 10 (Early Access)

[J5] \textbf{S. Kim}, M. Kim, J. Kim, S, Kim, and J. Park.
Grasping Force Prediction by EMG Signals and Arm Posture: Tensor Decomposition Based Approach,
Journal of Bionic Engineering, Vol. 16, No. 3, pp.  455-467, 2019.05

[J4] \textbf{S. Kim}, K. Jang, S. Park, Y. Lee, S. Y. Lee, and J. Park, Continuous Task Transition Approach for Robot Controller based on Hierarchical Quadratic Programming, IEEE Robotics and Automation Letters (with International Conference on Robotics and Automation 2019), Vol. 4, No. 2, pp. 1603-1610, 2019.05

[J3] \textbf{S. Kim}, M. Kim, J. Lee, S. Hwang, J. Chae, B. Park, H. Cho, J. Sim, J. Jung, H. Lee, S. Shin, M. Kim, W. Choi, Y. Lee, S. Park, J. Oh, Y. Lee, S. Lee, M. Lee, S. Yi, K. Chang, N. Kwak, and {J. Park}.
Team SNU’s Control Strategies to Enhancing Robot’s Capability: Lessons from the DARPA Robotics Challenge Finals 2015, The DARPA Robotics Challenge Finals: Humanoid Robots to the Rescue, Springer, pp. 347-379, 2018.04

[J2] \textbf{S. Kim}, M. Kim, J. Lee, S. Hwang, J. Chae, B. Park, H. Cho, J. Sim, J. Jung, H. Lee, S. Shin, M. Kim, W. Choi, Y. Lee, S. Park, J. Oh, Y. Lee, S. Lee, M. Lee, S. Yi, K. Chang, N. Kwak, and {J. Park}.
Team SNU’s Control Strategies to Enhancing Robot’s Capability: Lessons from the 2015 DARPA Robotics Challenge Finals. Journal of Field Robotics, Vol. 34, No. 2, pp. 359-380, 2017.03

[J1] \textbf{S. Kim}, M. Kim, J. Lee, and {J. Park}.
Robot Hand Synergy Mapping Using Multi-factor Model and EMG signal.
(with International Symposium on Experimental Robotics 2014), Springer, pp.671-683, 2015.11

\section{\sc International Conference Articles}
[C8] \textbf{S. Kim}, K. Jang, S. Park, Y. Lee, S. Y. Lee, and J. Park, Whole-body Control of Non-holonomic Mobile Manipulator Based on Hierarchical Quadratic Programming and Continuous Task Transition. IEEE International Conference on Advanced Robotics and Mechatronics (ARM), Osaka, Japan, 2019, \textbf{Best Conference Paper Award}

[C7] \textbf{S. Kim}, J. Kim, and J. Park.
Real-time Inverse Kinematics Technique for Controlling Humanoid Avatar with Redundant Arm,
Ubiquitous Robot 2018, Hawaii, USA, 2018.

[C6] M. Kim, J. Kim, \textbf{S. Kim}, J. Sim, and J. Park.
Disturbance Observer based Linear Feedback Controller for Compliant Motion of Humanoid Robot,
International Conference on Robotics and Automation (ICRA), Australia, 2018.

[C5] M. Kim, \textbf{S. Kim}, and {J. Park}.
Human Motion Imitation for Humanoid by Recurrent Neural Network.
The 13th International Conference on Ubiquitous Robots and Ambient Intelligence,
Xian, China, 19-22 Aug, 2017.


[C4] J. Jung, J. Kim, \textbf{S. Kim}, W. Kwon, S. Na, K. Kim, J. Lee, G. Suh, and J. Park.
Application of Robot Manipulator for Cardiopulmonary Resuscitation,  International Symposium on Experimental Robotics 2016, Springer, pp. 266-274, 2017.03

[C3] \textbf{S. Kim}, M. Kim, J. Lee, S. Hwang, J. Chae, B. Park, H. Cho, J. Sim, J. Jung, H. Lee, S. Shin, M. Kim, N. Kwak, Y. Lee, S. Lee, M. Lee, S. Yi, K. K.C. Chang, and {J. Park}.
Approach of Team SNU to the DARPA Robotics Challenge Finals.
2015 IEEE-RAS International Conference on Humanoid Robots,
Seoul, Korea, 3-5 Nov 2015.

[C2] M. Schwartz, S. Hwang, Y. Lee, J. Won, \textbf{S. Kim}, and {J. Park}.
Aesthetic Design and Development of Humanoid Legged Robot.
The 2014 IEEE-RAS International Conference on Humanoid Robots,
Madrid, Spain, 18-20 Nov 2014.

[C1] \textbf{S. Kim}, C. Lee, and J. Ryu.
Data-driven Haptic Rendering of Friction between Surgical Device and Trocar for Laparoscopic Surgery Simulator,
ACCAS 2010, Busan, Korea, 2010.

\section{\sc Domestic \\ Journal Articles}

[DJ6] K. Jang, \textbf{S. Kim}, S. Park, and J. Park.
Unified Framework for Overcoming Motion Constraints of Robots Using Task Transition Algorithm,
Journal of Korea Robotics Society, Vol. 13, No. 2, 2018.

[DJ5] J. Kim, \textbf{S. Kim}, and {J. Park}.
The Trends of HRI: Focusing on Task Oriented Robot User Interface,
Robot and Human, 
Vol. 14, No. 4, 2017.

[DJ4] \textbf{S. Kim} and {J. Park}.
Singularity Avoidance Algorithms for Controlling Robot Manipulator: A Comparative Study,
Journal of Korea Robotics Society, Vol. 12, No. 1, 2017. \textbf{Best Paper Award}

[DJ3] S. Shin, M. Kim, J. Ahn, \textbf{S. Kim}, and J. Park.
Development of Tele-operation Interface and Stable Navigation Strategy for Humanoid Robot Driving,
Journal of Institute of Control, Robotics and Systems, Vol. 22, No. 11, 2016.

[DJ2] \textbf{S. Kim}, B. Park, and {J. Park}.
DRC Finals 2015 – Analysis of Participants,
Robot and Human, 
Vol. 12, No. 4, 2015.

[DJ1] \textbf{S. Kim}, C. Lee, J. Kim, and J. Ryu.
Approximate Friction and Gravity Compensation in Haptic Laparoscopic Surgery Simulator,
Transactions of the KSME,
Vol. 35, No. 8, 2010.

\section{\sc Domestic Conference Articles}
[DC9] S. Park, K. Jang, S. Kim, \textbf{S. Kim}, and J. Park.
nverse Kinematics Minimizing JointsTorque with Given Target Wrench,
The 15th Korea Robotics Society Annual Conference (KROC), Korea, 2020.


[DC8] S. Y. Lee, S. Park, K. Jang, \textbf{S. Kim}, S. Kim, and J. Park.
A Comparative Study of Tracking Control with Closed Loop Inverse Kinematics Algorithm,
The 14th Korea Robotics Society Annual Conference (KROC), Korea, 2019.

[DC7] J. Jang, \textbf{S. Kim}, S. Park, S. Y. Lee, and J. Park
Self-collision Avoidance Algorithm for Robot Manipulator using Continuous Task Transition Algorithm, 
The 14th Korea Robotics Society Annual Conference (KROC), Korea, 2019.

[DC6] K. Jang, \textbf{S. Kim}, S. Park, and J. Park, 
Joint Limit Avoidance of Non-holonomic Mobile Manipulator using Weighting Matrix in Generalized Pseudo-Inverse, Conference on Korean Society for Precision Engineering, Korea, 2017.

[DC5] M. Kim, R. Destenay, \textbf{S. Kim}, J. Kwon, K. Yeom, {J. Park}, and B. You.
Avatar Motion Generation by Null-Space Mapping Based on Minimum Number of Markers.
2015 Conference on Information and Control Systems,
Sokcho, Korea, 2015.

[DC4] \textbf{S. Kim}, M. Kim, and J. Park.
Extracting Postural Synergies Using Grasping Taxonomy, 
The 9th Korea Robotics Society Annual Conference (KROC), Korea, 2014.

[DC3] J. Lee, M. Kim, \textbf{S. Kim}, and J. Park.
Estimation of Hand Posture and Grasping Force Using Surface EMG, 
The 9th Korea Robotics Society Annual Conference (KROC), Korea, 2014.

[DC2] \textbf{S. Kim}, C. Lee, J. Kim, and J. Ryu.
Friction and Gravity Compensation in Haptic Laparoscopic Surgery Simulator,
Conference on Korean Society of Mechanical Engineers (KSME), Korea, 2010.


[DC1] \textbf{S. Kim}, C. Lee, J. Kim, and J. Ryu.
Trocar Friction modelling for Friction and gravity Compensation,
Conference on Korean Society of Mechanical Engineers (KSME), Korea, 2010.

\section{\sc Workshops}
[W2] \textbf{S. Kim} and {J. Park}.
Control Strategies of Team SNU for DRC Finals, and Future Directions for Robots in Human Environment.
Invited speaker at Workshop on “What did we do for the DARPA Robotics Challenge?, 
2015 IEEE-RAS International Conference on Humanoid Robots,
Seoul, Korea, 3-5 Nov 2015.

[W1] \textbf{S. Kim}, J. Lee, M. Kim, and {J. Park}.
Teleoperated Robot Hand Control using Tensor Decomposition.
Full-day Tutorial on Robotics-based Methods for the Identification, Recognition, and Synthesis of Human Motions,
IEEE/RSJ International Conference on Intelligent Robots and Systems, 
Tokyo, Japan, 3 Nov 2013.

\section{\sc Ongoing Papers}

[O1] Y. Lee, \textbf{S. Kim},  J. Park, N. Tsagarakis, and J. Lee, EOS-WBC: Enhanced Operational-space Based Whole Body Control Framework under Inequality Constraints, Roboics and Autonomous Systems, under review, 2020.

[O2] S. Hong, K. Jang,  \textbf{S. Kim},  J. Park, Regularized Hierarchical Quadratic Program for Real-Time Whole Body Motion Generation, Transaction on Mechatronics, minor revision, 2020.

\section{\sc Academic \\Services}

Reviewer for IEEE Robotics and Automation Letters (RAL), 2015. \\
Reviewer for IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), 2018. \\
Reviewer for IEEE International Conference on Ubiquitous Robots (UR), 2018.\\
Reviewer for IEEE International Conference on Robotics and Automation (ICRA), 2019. \\
Reviewer for IEEE Robotics and Automation Letters (RAL), 2019. \\
Reviewer for IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), 2020. \\
\end{resume}
\end{document}




\grid
\grid
\grid
